Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-14 SI.tex
update figures befor sending to Elton

\pagebreak{}
\section{Comment on the hypothetical ``dielectric constant'' in the effective medium theory (EMT)}
\label{sec:2D-3D-rescale}
From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. Such method makes use of the
effective medium theory (EMT), and as discussed in the main text, the
definition of the 2D ``dielectric constant'' is questionable, due to
the locality of electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Moreover, the
EMT approach assumes that the 2D material has an effective thickness
$\delta$ and effective dielectric constant
$\varepsilon_{\mathrm{2D}}$, while the exact value of $\delta$ is
unknown due to the ambiguity of the reference planes. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical. On
the contrary, the 2D polarizability approach presented in the main
text is independent of the choice of the parameter $\delta$, as well
as the volume fraction of the 2D material, and can correctly capture
the dielectric properties of the 2D material.

In brief, the hypothetical 2D dielectric constant
$\varepsilon$ comes from the planar limit of the
effective medium theory \cite{Markel_2016,Aspnes_1982}, and can be
expressed by means of the macroscopic dielectric constant
$\varepsilon_{\mathrm{SL}}$ of the superlattice:

\begin{eqnarray}
  \label{eq:MG-effect-1}
  &\varepsilon_{\mathrm{SL}}^{\parallel} &= f \varepsilon_{\mathrm{2D}}^{\parallel} + (1 - f)\\
  \label{eq:MG-effect-2}
  &(\varepsilon_{\mathrm{SL}}^{\perp})^{-1} &= f /\varepsilon_{\mathrm{2D}}^{\perp} + (1-f)
\end{eqnarray}
where $f=\delta/L$ is the volume fraction of the 2D
material in the superlattice and $\varepsilon_{\mathrm{2D}}^{\parallel}$ and 
$\varepsilon_{\mathrm{2D}}^{\perp}$ are the corresponding dielectric constants for the 2D layer. 
The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}$. To
eliminate the modeling error caused by the \textit{a priori} parameter
selection of $\delta$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.

@@

As can be seen from the fitted results in Figure
\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}$ extracted
from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ are close when $L> 15$
{\AA}. Notably, the $\delta_{\mathrm{2D}}$ values are generally 10\%
smaller than the interlayer distance in corresponding bulk materials
$L_{\mathrm{bulk}}$ , as shown in Table \ref{tab:delta-L-DFt}. On the
other hand, the extracted $\delta_{\mathrm{2D}}$ values are closer to
the covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ as
described in the main text, with a difference generally smaller than
5\%. Our results indicate that the conventional estimation of the 2D
layer thickness by its bulk interlayer distance
\cite{Matthes_2016,Laturia_2018}, will always lead to
overestimation. On the contrary, the out-of-plane polarizability
$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness nature
of 2D materials.

\begin{table}[htbp]
  \centering
  \begin{tabular}[htbp]{lccccc}
  \hline{}
  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ ({\AA})\\
  \hline{}
  2H-MoS$_{2}$ & 5.76 & 5.49 & 6.15 & 5.22 & 4.98\\
  2H-MoSe$_{2}$ & 5.98 & 5.92 & 6.46 &  5.73 & 5.60\\
  2H-MoTe$_{2}$ & 6.43 & 6.85 & 6.98 & 6.37 & 6.12\\
  2H-WS$_{2}$ & 5.63 & 5.49 & 6.15 & 5.20 & 5.00\\
  2H-WSe$_{2}$ & 5.84 & 5.92 & 6.49 & 5.75 & 5.42\\
  2H-WTe$_{2}$ & 6.32 & 6.58 & 7.06 & 6.38 & 6.33\\
  \hline{}
\end{tabular}

\caption{Calculated $\delta_{\mathrm{2D}}$ from
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$, compared with the interlayer
  distance of corresponding bulk material $L_{\mathrm{SL}}$, the
  covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, and
  $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
\label{tab:delta-L-DFt}
\end{table}

Another drawback of the 2D EMT approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\linewidth]{img/SI-eps-alpha-error.pdf}
  \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
    function of the difference between $\delta_{\mathrm{2D}}$ and
    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$. A small change of
    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
    the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
    which is apparently unphysical}
  \label{fig:eps-alpha-error}
\end{figure}

which indicate that the characteristic length
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}$ and
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the guess of the thickness, and therefore is the true descriptor of
the 2D dielectric nature.

To conclude, based on theoretical and technical considerations, there are several
advantages of using the polarizability $\alpha$ for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ in EMT requires calculation with varied superlattice length.
\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.

@@

\section{More discussions about the dielectric anisotropy}
\label{sec:aniso}
\subsection{The 2D screening length}
\label{ssec:2D-screening}
Here we show a schematic drawing of the polarizability ellipsoid for a
2D material in Figure \ref{fig:ellipsoid}. As can be seen the
polarizability ellipsoid is ultraflat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, which is the origin of the high
dielectric anisotropy of 2D materials.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\linewidth]{img/SI-ellipsoid.pdf}
  \caption{Polarizability ellipsoid of a 2D material, the long axis
    equals $\alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ and the short axis
    equals  $\alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$}
  \label{fig:ellipsoid}
\end{figure}

@@

>>>>

\pagebreak{}
\section{Further Data Concerning the Comparison with EDM}
\label{sec:2D-3D-rescale}

The major issue when using such rescale
relations comes from the determination of $\delta_{\mathrm{2D}}^{*}$. To
eliminate the modeling error caused by the \textit{a priori} parameter
selection of $\delta$, we perform the calculation of
$\varepsilon_{\mathrm{SL}}$ of group 6 TMDCs against different $L$,
and use least-square fitting to extract both
$\varepsilon$ and $\delta$, as shown in
Figure \ref{fig:rescale-prb}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/SI-alpha-convergence.pdf}
  \caption{Convergence of electronic polarizabilities
    $\Delta \varepsilon_{\mathrm{2D}}^{\parallel}$ (\textbf{a}) and
    $\Delta \varepsilon_{\mathrm{2D}}^{\perp}$ (\textbf{b}) as
    functions of $L$ for the selected TMDCs, respectively. For both
    in- and out-of-plane polarizabilities, convergence is achieved
    when $L >$15 \AA{}}
  \label{fig:alpha-converg}
\end{figure}

@@

As can be seen from the fitted results in Figure
\ref{fig:rescale-prb}, the values of $\delta_{\mathrm{2D}}^{*}$ extracted
from both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ are close when $L> 15$
{\AA}. Notably, the $\delta_{\mathrm{2D}}^{*}$ values are generally 10\%
smaller than the interlayer distance in corresponding bulk materials
$L_{\mathrm{bulk}}$ , as shown in Table \ref{tab:delta-L-DFt}. On the
other hand, the extracted $\delta_{\mathrm{2D}}^{*}$ values are closer to
the covalent thickness $\delta_{cov}$ as
described in the main text, with a difference generally smaller than
5\%. Our results indicate that the conventional estimation of the 2D
layer thickness by its bulk interlayer distance
\cite{Matthes_2016,Laturia_2018}, will always lead to
overestimation. On the contrary, the out-of-plane polarizability
$\alpha_{\mathrm{2D}}^{\perp}$ correctly captures the thickness nature
of 2D materials.

\begin{table}[htbp]
  \centering
  \begin{tabular}[htbp]{lccccc}
  \hline{}
  Material & $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$ (\AA) & $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ ({\AA})& $L_{\mathrm{Bulk}}$ ({\AA}) & $\delta_{\mathrm{cov}}$ ({\AA}) & $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ ({\AA})\\
  \hline{}
  2H-MoS$_{2}$ & 5.76 & 5.49 & 6.15 & 5.22 & 4.98\\
  2H-MoSe$_{2}$ & 5.98 & 5.92 & 6.46 &  5.73 & 5.60\\
  2H-MoTe$_{2}$ & 6.43 & 6.85 & 6.98 & 6.37 & 6.12\\
  2H-WS$_{2}$ & 5.63 & 5.49 & 6.15 & 5.20 & 5.00\\
  2H-WSe$_{2}$ & 5.84 & 5.92 & 6.49 & 5.75 & 5.42\\
  2H-WTe$_{2}$ & 6.32 & 6.58 & 7.06 & 6.38 & 6.33\\
  \hline{}
\end{tabular}

\caption{Fitted effective thickness
  $\delta_{\mathrm{2D}}^{\parallel, \mathrm{fit}}$ and
  $\delta_{\mathrm{2D}}^{\perp, \mathrm{fit}}$ from in- and
  out-of-plane dielectric data, compared with the interlayer distance
  of corresponding bulk material $L_{\mathrm{Bulk}}$, the covalent
  thickness $\delta_{\mathrm{cov}}$, and
  $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ for 2H TMDC
  materials.}
\label{tab:delta-L-DFt}
\end{table}

One main drawback of the EDM approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\linewidth]{img/SI-eps-alpha-error.pdf}
  \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
    function of the difference between $\delta_{\mathrm{2D}}^{*}$ and
    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$. A small change of
    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
    the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
    which is apparently nonphysical.}
  \label{fig:eps-alpha-error}
\end{figure}

which indicate that the characteristic length
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}^{*}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}^{*}$ and
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}^{*}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the guess of the thickness, and therefore is the true descriptor of
the 2D dielectric nature.

To conclude, based on theoretical and technical considerations, there are several
advantages of using the electronic polarizability for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ in EMT requires calculation with varied superlattice length.
\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.

@@

\section{More discussions about the dielectric anisotropy}
\label{sec:aniso}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
